---
title: "P8105 Homework 1"
author: "Rebekah Hughes"
date: 2020-09-15
output: git_document
---

## Problem 1

The following code creates a data frame, labeled as "hw1_p1_df", with four variables, including a random sample that follows a normal distribution of sample size 10, a logical vector indicating elements greater than 0 as "true", a character vector of length 10 and a factor vector of length 10 and with 3 different levels.

```{r, results = 'hide'}
library (tidyverse)
hw1_p1_df = tibble (
  rand_samp = rnorm (10, sd = 0.5),
  rand_samp_pos = rand_samp > 0,
  rand_samp_char = c("Apple", "Lemon", "Lime", "Pear", "Plum", "Peach", "Berry", "Cherry", "Mango", "Melon"),
  rand_samp_fact = factor (c("red", "yellow", "green", "yellow", "red", "red", "red", "red", "yellow", "green")))
```

The data frame created has 10 observations and 4 variables.

Below, the means of each of the 4 variables from the data frame is computed.

```{r, warning = false}
rand_samp_av = mean (pull (hw1_p1_df, rand_samp))
log_av = mean (pull (hw1_p1_df, rand_samp_pos))
char_av = mean (pull (hw1_p1_df, rand_samp_char))
fact_av = mean (pull (hw1_p1_df, rand_samp_fact))
```

Of the above mean calculations, only the means for the random sample and the logical vector variables were able to be determined becasue they are numeric.




